Describe Participants: Characteristics, Diet, and Cardiometabolic Risk

### 2022-01-06 Rmarkdown/analysis/Characteristics_Diet_CardiometabolicRisk_211111.Rmd
Calculate total mps for male and females

>>>>

# Total of meat, poultry, seafood, organ meat, and cured meat (oz. eq.) - MALES
summary(full$pf_mps_total_totals[full$sex == "Male"])
sd(full$pf_mps_total_totals[full$sex == "Male"])
# Total of meat, poultry, seafood, organ meat, and cured meat (oz. eq.) - FEMALES
summary(full$pf_mps_total_totals[full$sex == "Female"])
sd(full$pf_mps_total_totals[full$sex == "Female"])
